---
title: "Snippets"
description: |
  Little bits of code. 
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
```

This is a place where I will put little bits of useful code with examples...for you to learn from, and for me to remember!  

Unfortunately, I have lost the references to most of them, so to those of you out there who figured these out first, thanks & sorry!


# Pipelining a wildcard in a filter{#wildcardFilter}
2022-12-25

So here is the scenario. I have a data frame like so:

```{r, echo=TRUE}
df <- tribble(
  ~doc, ~val,
  'B',1,
  'B',2,
  'BC',1,
  'BC',4,
  'D',5
)

df
```

and I want to do a filter in a long sequence of code. But I want to be able to find all rows if the user enters 'ALL', or just the matching rows if they enter something else. So 'ALL' acts like a wildcard.

For example, if the user enters (say into a variable _docname_) _B_, I want the pipelline to return the first two rows. But if they enter _ALL_, I want all rows returned.

Here is how to do it.

```{r, echo=TRUE}
docname<-'B'
df %>% {if(docname!='ALL') filter(., doc == docname) else .} 
```

```{r, echo=TRUE}
docname<-'BC'
df %>% {if(docname!='ALL') filter(., doc == docname) else .} 
```

```{r, echo=TRUE}
docname<-'ALL'
df %>% {if(docname!='ALL') filter(., doc == docname) else .} 
```




# Labelling in latex{#latexLabelling}
2022-12-25

When writing a mathy document, it can be helpful to explain what each part of an equation means. _underbrace_ and _text_ are your friends.

Here is an example


$$y=\underbrace{3 \alpha}_\text{What alpha means}\times \underbrace{f\left( x^3\right)}_\text{why x cubed?}$$
The latex is:
```
y=\underbrace{3 \alpha}_\text{What alpha means}\times \underbrace{f\left( x^3\right)}_\text{why x cubed?}
```





